Technical Report

### 2018-01-19 fully-abstract-comp/technical-report.tex
typos in proposed ft world relation

\subsection{Future world}
\subsubsection{\color{green} first thoughts on change to future world relation}
{\color{green}
The public part of the future world relation stays the same:
\begin{mathpar}
  \inferrule{ \exists m : \RegionName \fun \RegionName, \text{ injective}\ldotp \dom(W') \supseteq \dom(m(W)) \wedge \forall r \in \dom(W)\ldotp W'(m(r)) \pubft W(r) }
            { W' \future W }
\end{mathpar}
The private future world relation becomes:
\begin{mathpar}
  \inferrule{ \exists m : \RegionName \fun \RegionName, \text{ injective}\ldotp \dom(W') \supseteq \dom(m(W)) \wedge \forall r \in \dom(W)\ldotp W'(m(r)) \privft W(r) \\  \exists r \in \dom(W') \cap \dom(W)\ldotp W'(r) \text{ is non-empty and stack region}}
            { W' \future W }
\end{mathpar}
where we take "is non-empty and stack region" to mean the following:

@@

\begin{definition}
  We say a region $(k,s,\phi_\pub,\phi,H)$ is a stack region on a machine with starting stack domain $[\stkb,\eaddr]$ iff
\[
  \begin{array}{l}
    \forall n, \hat{W},s'\ldotp \forall \npair{\stpair{\ms}{\ms}} \in H \; s' \; \hat{W} \ldotp \dom(\src{\ms_S}) \subset [\stkb,\eaddr]  \wedge \dom(\ms_T) \subset [\stkb,\eaddr]
  \end{array}
\]
\end{definition}

}

>>>>

\subsection{Future world}
\subsubsection{\color{green} first thoughts on change to future world relation}
{\color{green}
The public part of the future world relation stays the same:
\begin{mathpar}
  \inferrule{ \exists m : \RegionName \fun \RegionName, \text{ injective}\ldotp \dom(W') \supseteq \dom(m(W)) \wedge \forall r \in \dom(W)\ldotp W'(m(r)) \pubft W(r) }
            { W' \future W }
\end{mathpar}
The private future world relation becomes:
\begin{mathpar}
  \inferrule{ \exists m : \RegionName \fun \RegionName, \text{ injective}\ldotp \dom(W') \supseteq \dom(m(W)) \wedge \forall r \in \dom(W)\ldotp W'(m(r)) \privft W(r) \\  \exists r \in \dom(W') \setminus \dom(m(W))\ldotp W'(r) \text{ is non-empty and stack region}}
            { W' \future W }
\end{mathpar}
where we take "is non-empty and stack region" to mean the following:

@@

\begin{definition}
  We say a region $(k,s,\phi_\pub,\phi,H)$ is a stack region on a machine with starting stack domain $[\stkb,\eaddr]$ iff
\[
  \begin{array}{l}
    \forall n, \hat{W},s'\ldotp \forall \npair{\stpair{\ms}{\ms}} \in H \; s' \; \hat{W} \ldotp \dom(\src{\ms_S}) \subseteq [\stkb,\eaddr]  \wedge \dom(\ms_T) \subseteq [\stkb,\eaddr]
  \end{array}
\]
\end{definition}
}
